A Large-scale Study of Polymorphism in R

### 2019-03-21 paper/main.tex
minor

@@

\newpage
\section{The Corpus}\label{sec:corpus}

@@

In this section, we will detail our methodology for collecting data.

The basic idea we are exploring is to observe arguments and return values of
function calls, and from these generalize possible type signatures for the
called functions. To this end, we build on an open source tool called
\genthat whose purpose was to generate unit tests for R
libraries~\cite{issta18}.  To generate test cases, one must record and
recreate accurately arguments and return values and avoid generating
redundant tests (i.e. tests that do not increase code coverage). For our
purposes, we change the existing tool in two main ways, we record argument
\emph{shapes} rather than their values, given the limited number of shapes
this allowed us to avoid having to run code coverage minimization phase of
the tool. Both changes were beneficial for scalability -- allowing us to
trace more calls than was reported in~\cite{issta18}.

@@

To illustrate our approach consider the following script which adds a double
to an integer, and the creates a matrix and a vector to i.

@@

tracer, which we
modified to capture the type information of arguments.  {\tt genthat}
generates traces for each unique function invocation with the express
purpose of re-invoking the function at a later time, and instead of
generating traces for these invocations we capture type information of the
arguments and return values of functions.  This is done by evaluating the
arguments and return values of functions at the end of the function's scope
in the relevant environment.  The sort of types and granularity of the type
information that are generated can be specified in our tracer: Essentially,
our tracer is parameterized over a user-specified type system.  For
instance, if desired our tracer can dig into lists and data frames to get
the types of list elements and fields.  Our tracer produces trace results
for each unique type signature encountered, which may then be used for data
analysis.

%
The high-level process for tracing one package is as follows:

>>>>

In R, function can be called with named parameters, R support variable
argument lists, and arguments can have default values. Putting all of these
together consider the following declaration:

\begin{lstlisting}[style=R]
f <- function(x, ..., y=3) x + y
\end{lstlisting}

\noindent
Function \k{f} can be called with a single argument \code{f(3)}, with named
argument \code{f(y=4,x=2)} and with a variable number of arguments,
\code{f(1,2,3,4,y=5)}, all of these calls will return \code{6}.

@@

\newpage
\section{Corpus}\label{sec:corpus}

@@

In this section, we will detail our methodology for collecting data.  The
basic idea we are exploring is to observe arguments and return values of
function calls, and from these generalize possible type signatures for the
called functions. To this end, we build on an open source tool called
\genthat whose purpose was to generate unit tests for R
libraries~\cite{issta18}.  To generate test cases, one must record and
recreate accurately arguments and return values and avoid generating
redundant tests (i.e. tests that do not increase code coverage). For our
purposes, we change the existing tool in two main ways, we record argument
\emph{shapes} rather than their values, given the limited number of shapes
this allowed us to avoid having to run code coverage minimization phase of
the tool. Both changes were beneficial for scalability -- allowing us to
trace more calls than was reported in~\cite{issta18}.

@@

To illustrate our approach consider the following script which adds a double
to an integer, and then creates a matrix and a vector, adds them together to
yield a new matrix.

@@

>>>>

The high-level process for tracing one package is as follows:
